04_LDA_v2

### 2019-12-25 analysis/04_LDA_v2.Rmd
new figs

  train.data <- left_join(trainsamples, traindata) %>%
    dplyr::select(-V1, -bird, -tissue, -group, -study, - treatment)

@@

  test.data <- testdata

@@

  # LDA analysis
  # Fit the model
  model <- lda(newgrouping~ ., data = train.transformed)
  # Make predictions
  predictions <- model %>% predict(test.transformed)

@@

```

```{r LDApredictions}

df1 <- LDA.hyp %>% distinct(treatment, predictedstage) %>%
  group_by(treatment) %>%
  summarize(predictedstages = str_c(predictedstage , collapse = ", "))  %>%
  mutate(tissue = "hypothalamus") 
kable(df1)

>>>>

  train.data <- left_join(trainsamples, traindata) %>%
    dplyr::select(-V1, -bird, -tissue, -group, -study, -treatment)

@@

@@

  # LDA analysis
  # Fit the model
  model <- lda(newgrouping ~ ., data = train.transformed)
  # Make predictions
  predictions <- model %>% predict(test.transformed)

@@

plot_grid(a,b,c, rel_heights = c(1.6,1,1.2), nrow = 3)
```

```{r LDApredictions}
df1 <- LDA.hyp %>% distinct(treatment, predictedstage) %>%
  group_by(treatment) %>%
  summarize(predictedstages = str_c(predictedstage , collapse = ", "))  %>%
  mutate(tissue = "hypothalamus") 
kable(df1)
